\documentclass[12pt]{article}
\usepackage[pdftex]{graphicx}
\usepackage{hyperref}
\hypersetup{pdfauthor={Alain Reguera Delgado},%
            pdftitle={Anaconda Progress Visual Style},%
            pdfsubject={CentOS Corporate Visual Identity}%
            }

% Tell LaTeX how to hyphenate a word. Don't hyphenate the following
% words:
\hyphenation{CentOS CENTOSARTWORK}

\title{Anaconda Progress Visual Style}
\author{Alain Reguera Delgado}

\begin{document}

\maketitle

\begin{abstract}

This article describes the visual style of Anaconda Progress.
Anaconda Progress screen is shown after configuration and while
packages are installed. Anaconda Progress screen has a header, and
slide images which alternate with release notes texts.  This article
describes Anaconda Progress slide images and release notes only.  The
header component of Anaconda Progress is described in the document
``Anaconda Header Visual Style''.

Anaconda is the name of the install program used by CentOS.  It is
python-based with some custom modules written in C. The Anaconda
installer works on a wide variety of Linux-based computing
architectures (ia32, Itanium, Alpha, S/390, PowerPC), and is designed
to make it easy to add platforms.

Copyright \copyright\ 2010 The CentOS Project. Permission is granted
to copy, distribute and/or modify this document under the terms of the
GNU Free Documentation License, Version 1.2 or any later version
published by the Free Software Foundation; with no Invariant Sections,
no Front-Cover Texts, and no Back-Cover Texts. A copy of the license
is included in the section entitled ``GNU Free Documentation
License''.  

\end{abstract}

\tableofcontents

\input{sections/introduction.tex}
\input{../../../../../installation.tex}
\input{../../../../../configuration.tex}
\input{sections/framework.tex}
\input{sections/rebranding.tex}

\input{../../../../../Licenses/GFDL.tex}

\end{document}
