\section{Rebranding}

\subsection{Package: redhat-logos}

The \texttt{redhat-logos} package contains files created by the CentOS
Project to replace the Red Hat ``Shadow Man'' logo and  RPM logo.  The
Red Hat ``Shadow Man'' logo, RPM, and the RPM logo are trademarks or
registered trademarks of Red Hat, Inc. Firstboot images that need to
be rebranded in \texttt{redhat-logos} package are illustrated in
\autoref{fig:Distribution:Anaconda:Firstboot:Rebranding:Logos}.

Replacements for these files are available in the Firstboot image
directory (
\autoref{sec:Distribution:Anaconda:Firstboot:Identity:Images}) of
Firstboot (\autoref{cha:Distribution:Anaconda:Firstboot}) inside your
working copy of CentOS Artwork Repository.

Once you rebrand the image files inside the SRPM package, you need to
rebuild it with the new brand information.

\subsection{Package: redhat-artwork}

The \texttt{redhat-artworks} package contains the themes and icons
that make up the CentOS default look and feel.  Relevant files to
firstboot rebranding are described below:

The following files in \texttt{redhat-artwork} need to be rebranded:

Once you rebrand the image files inside the \texttt{redhat-artwork}
SRPM package, you need to rebuild it with the new brand information.

\subsection{Package: firstboot}

Firstboot messages locale contains the upstream brand, so they need to
be rebranded too. The .po files you need to rebrand are inside the
firstboot package.  The \texttt{firstboot} package contains the
firstboot utility that runs after installation.  Once you rebrand the
content of .po files inside \texttt{firstboot} SRPM package, you need
to rebuild it with the new brand information.  The rebranded .mo files
are created in the installation process.

\subsection{Package: firstboot-tui}

The \texttt{firstboot-tui} package contains a text interface for the
\texttt{firstboot} package.  Once you rebrand the content of
\texttt{.po} files inside the \texttt{firstboot-tui} SRPM package, you
need to rebuild it with the new brand information.  The rebranded
\texttt{.mo} files are created in the installation process.

\subsection{Package: centos-release}

The CentOS License Agreement, shown after the welcome screen of
firstboot, is controled by the file \texttt{eula.en\_US} which is
controlled by the \texttt{centos-release} package.  The
\texttt{centos-release} package contains the CentOS release notes and
eula files.

The file \texttt{eula.en\_US} contains the English translation of
CentOS License Agreement. English language is the reference for
specific language translations of CentOS License Agreement. Specific
language translations of CentOS License Agreement are accepted by
Firstboot in the path \texttt{/usr/share/eula/}. 

File names of eula specific language translations should have the
format \texttt{eula.lang} or \texttt{eula.lang\_COUNTRY}.  Where
\texttt{lang} is a two-lowercase-letters code representing the
translation language and \texttt{COUNTRY} a two-uppercase-letters code
representing the country of that translation language. Languages' and
countries' codes are specified as described in the standards ISO639
and ISO3166 respectively.

When using Anaconda in a language different from English firstboot
checks if there is any eula translation file for the currenct
language. If so, the specific language eula file is loaded and shown
to the user.  Otherwise the \texttt{eula.en\_US} file is used.

The CentOS eula files, described in the previous list, have their own
framework inside CentOS Artwork Repository. They are rendered similar
to images using templates and translation files, as well as rendering
scripts. 

The files \texttt{EULA} and \texttt{eula.en\_US} should have the same
information. The \texttt{GPL} file contains the GPL license with a
brief description of how it applies to CentOS Distribution.

Once you rebrand the text files inside the \texttt{centos-release}
SRPM package, you need to rebuild it with the new brand information.

\begin{figure}[!hbp]
\hrulefill
\begin{verbatim}
/usr/share/firstboot/pixmaps/
|-- shadowman-round-48.png
\end{verbatim}
\hrulefill
\caption{Firstboot rebranding (package: redhat-logos)%
   \label{fig:Distribution:Anaconda:Firstboot:Rebranding:Logos}}
\end{figure}

\begin{figure}[!hbp]
\hrulefill
\begin{verbatim}
/usr/share/firstboot/pixmaps/
|-- firstboot-left.png
|-- splash-small.png
\end{verbatim}
\hrulefill
\caption{Firstboot rebranding (package: redhat-artwork)%
   \label{fig:Distribution:Anaconda:Firstboot:Rebranding:Artwork}}
\end{figure}

\begin{figure}[!hbp]
\hrulefill
\begin{verbatim}
/usr/share/eula/
|-- eula.en_US
/usr/share/doc/centos-release-5/
|-- EULA
|-- GPL
\end{verbatim}
\hrulefill
\caption{Firstboot rebranding (package: centos-release)%
   \label{fig:Distribution:Anaconda:Firstboot:Rebranding:Release}}
\end{figure}
\begin{verbatim}
\end{verbatim}
