\documentclass{article}
\usepackage{longtable}
\usepackage[pdftex]{graphicx}
\usepackage{hyperref}
\hypersetup{pdfauthor={CentOS Documentation SIG},%
            pdftitle={KDE Splash)},%
            pdfsubject={CentOS Corporate Visual Identity}%
            }

\title{KDE Splash}
\author{CentOS Documentation SIG}

\begin{document}

\maketitle

\begin{abstract} 

This article describes the KDE Splash Visual Style for CentOS
Distribution.  This image is displayed after login screen, while KDE
session is being loaded. 

Copyright \copyright\ 2010\ The CentOS Project. Permission is
granted to copy, distribute and/or modify this document under the
terms of the GNU Free Documentation License, Version 1.2 or any later
version published by the Free Software Foundation; with no Invariant
Sections, no Front-Cover Texts, and no Back-Cover Texts. A copy of the
license is included in the section entitled ``GNU Free Documentation
License''.  
\end{abstract}

\tableofcontents


\section{Workplace}
\begin{itemize}
\item SVN:trunk/Identity/Themes/\$THEME/Distro/BootUp/KSplash/
\item SVN:trunk/Translations/Identity/Themes/Distro/BootUp/KSplash/
\item SVN:trunk/Scripts/Identity/Themes/Distro/BootUp/KSplash/
\end{itemize}

\section{Theme}

\input{table-theme.tex}

\section{Design}

KDE Splash Preview.png and splash\_top\_bar.png images are rendered
for each major release of CentOS Distribution.  Each image is based in
the same Artistic Motif and has the following components:

\begin{enumerate}
\item The CentOS Symbol.
\item The CentOS Release Brand.
\item The CentOS Default Artistic Motif.
\end{enumerate}

KDE Splash splash\_inactive\_bar.png and splash\_active\_bar.png are
used to create the progress effect while loading. They both have the
same background color.

KDE Splash splash\_bottom\_bar.png is used to as background to the
label shown in the bottom. This image has the same background color of
splas\_inactive\_bar.png and splash\_active\_bar.png.

KDE Splash theme definitions are in the file Theme.rc. Among available
definitions are the splash  name, description, version, author,
engine, icons flashing, always show progress, and label foreground.

Image rendering is done using the script render.sh available in the
workplace.  This script creates the appropriate PNG images under
img/\$VERSION/.

There is no color limitation in this section.

\section{Configuration}

\input{table-config.tex}

\begin{description}

\item[Theme]: Defines the default splash theme. The name should match
a directory name under /usr/share/ksplash/Themes/.

\texttt{Theme=Modern}
\end{description}

\section{Rendering}
\section{Testing}
\section{Issues}

% License section
\input{../../../../../Licenses/GFDL.tex}

\end{document}
