\documentclass{article}
\usepackage{longtable}
\usepackage[pdftex]{graphicx}
\usepackage{hyperref}
\hypersetup{pdfauthor={CentOS Documentation SIG},%
            pdftitle={GNOME Splash)},%
            pdfsubject={CentOS Corporate Visual Identity}%
            }

\title{GNOME Splash}
\author{CentOS Documentation SIG}

\begin{document}

\maketitle

\begin{abstract} 

This article describes the GNOME Splash Visual Style for CentOS
Distribution. By default this image is disabled to make GNOME session
load faster. If you enable it,\footnote{To enable GNOME Splash image
go to: \texttt{System > Preferences > More Preferences > Sessions} and
check the item \texttt{Show splash screen on login}.} this image is
displayed after login screen, and while GNOME session is being loaded. 

Copyright \copyright\ 2010\ The CentOS Project. Permission is
granted to copy, distribute and/or modify this document under the
terms of the GNU Free Documentation License, Version 1.2 or any later
version published by the Free Software Foundation; with no Invariant
Sections, no Front-Cover Texts, and no Back-Cover Texts. A copy of the
license is included in the section entitled ``GNU Free Documentation
License''.  
\end{abstract}

\tableofcontents

\section{Workplace}
\begin{itemize}
\item SVN:trunk/Identity/Themes/\$THEME/Distro/BootUp/GSplash/
\item SVN:trunk/Translations/Identity/Themes/Distro/BootUp/GSplash/
\item SVN:trunk/Scripts/Identity/Themes/Distro/BootUp/GSplash/
\end{itemize}

\section{Theme}

\input{table-theme.tex}

\section{Design}

GNOME Splash is rendered for each major release of CentOS
Distribution. Each image is based in the same Artistic Motif and has
the following components:

\begin{enumerate}
\item The CentOS Symbol.
\item The CentOS Release Brand.
\item The CentOS Default Artistic Motif.
\end{enumerate}

Image rendering is done using the script render.sh available in the
workplace.  This script creates the appropriate PNG images under
img/\$VERSION/.

There is no color limitation in this section.

\section{Configuration}
\section{Rendering}
\section{Testing}
\section{Issues}

% License section
\input{../../../../../Licenses/GFDL.tex}

\end{document}
