% Part   : Concepts
% Chapter: Frameworks
% ------------------------------------------------------------
% $Id: files.tex 6044 2010-07-11 07:49:09Z al $
% ------------------------------------------------------------

\section{File Types} 

Inside CentOS Artwork Repository, there are ``image files'' and ``text
files''.

\subsection{Image Files} 
\hypertarget{sec:Concepts:Frameworks:Image}{}

Image files are used to implement the CentOS visual style on all
CentOS visual manifestations where image files  are involved (i.e.
CentOS distribution, CentOS web sites, CentOS promotion, etc.).  Image
files are inside identity frameworks.

Image files may be available in different formats. Image files in
different formats are produced taking the PNG format as base. The PNG
format is the Inkscape's export format used by \texttt{render.sh}
indentity script to produce a image copy of the SVG design templates.
The \texttt{render.sh} identity script uses command line image
manipulation tools, like ImageMagick and Netpbm, to do image format
convertions from PNG to the formats you specify.  You can produce as
many image formats as supported by the previously mentioned command
line image maipulation tools.  

Image files production in different formats is specified inside
configuration scripts, specifically in the variable
\hyperlink{sec:Concepts:Scripts:Configuration:ACTIONS}{\texttt{ACTIONS}}
(\autoref{sec:Concepts:Scripts:Configuration:ACTIONS}).

Inside frameworks, image files are stored in a directory named `img'.
This name is a convenction that scripts use to store framework's
produced images. If you want to change the image directory's name to
something different from `img', you need to set the same name in all
images' directories along the CentOS Artwork Repository, and update
scripts to recognize the new name you set.  This is something you
problably don't need to do, but if you still want to, please share
your reasons in
\href{mailto:centos-devel@centos.org}{centos-devel@centos.org} before
commit your changes. Changing the image directory's name is a big
chanage that needs to be discussed in the community.

\subsection{Text Files}
\hypertarget{sec:Concepts:Frameworks:Files:Text}{}

Text files are used to implement the CentOS visual style on all CentOS
visual manifestations where text files are involved (i.e.  eula files
and release notes used by Anaconda, etc.). Text files are inside
identity frameworks.
